\documentclass[12pt]{beamer}

\usepackage{color}

\usetheme{Pittsburgh}
\usecolortheme{seahorse}

\setbeamertemplate{enumerate items}[default]
\setbeamertemplate{itemize items}[circle]

%% ----------------------------------------------------------------------  

\begin{document}

%% ----------------------------------------------------------------------  

\author[D.C.~Ernst]{Dana C.~Ernst, Northern Arizona University}
\institute{\url{http://danaernst.com}}

%% ----------------------------------------------------------------------  

\begin{frame}

\begin{block}{Directions}
\begin{itemize}
\item Get in groups of size 3--4.
\item Group members should introduce themselves.
\item For each of the questions that follow, I will ask you to:
\begin{enumerate}
\item \textbf{Think} about a possible answer on your own.
\item \textbf{Discuss} your answers with the rest of your group.
\item \textbf{Share} a summary of each group's discussion.
\end{enumerate}
\end{itemize}
\end{block}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Question One}}


\parbox{\linewidth}{\begin{center}
\Huge Why are we here?
\end{center}}

\pause

\begin{center}

This question is way too vague!

Let's try a slightly better question.

\end{center}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Question One Improved}}

\parbox{\linewidth}{\begin{center}
\Huge What are the goals of a university education?
\end{center}}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Question Two}}

\parbox{\linewidth}{\begin{center}
\Huge Given that one can read and study on one's own, what is the point of going to university?
\end{center}}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Claim 1}}

\parbox{\linewidth}{\begin{center}
\Huge If I were to teach you all known information, it wouldn't last the year.
\end{center}}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Question Three}}

\parbox{\linewidth}{\begin{center}
\Huge How does a person learn something new?
\end{center}}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Question Four}}

\parbox{\linewidth}{\begin{center}
\Huge What do you reasonably expect you will remember from your courses in 20 years?
\end{center}}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Question Five}}

\parbox{\linewidth}{\begin{center}
\Huge What is the value of making mistakes in the learning process?
\end{center}}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Claim 2}}

\parbox{\linewidth}{\begin{center}
\Huge ``Any creative endeavor is built on the ash heap of failure."\\ -- Michael Starbird
\end{center}}

\end{frame}

%% ----------------------------------------------------------------------

\begin{frame}{\textbf{Question 6}}

\parbox{\linewidth}{\begin{center}
\Huge How do we create a safe environment where risk taking is encouraged and productive mistakes are valued?
\end{center}}

\end{frame}


%% ----------------------------------------------------------------------

\end{document}